---
title: "REDCapQC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{REDCapQC_Vig}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(REDCapQC)
```

The function REDCapQC requires two inputs:

  (1) directory with both the REDCap data dictionary and REDCap data export

  (2) dataset name after saving the dataset as an R dataset

Assumptions for inputs:

  * The program will require the CSV data dictionary from REDCap with the name unchanged
  * An all data export from REDCap that has been saved
  * Example: save(myData, file=“/myData.Rdata”)
  * All files are in the specified working directory
  * Only required fields will undergo QC
  * All dates fields will be given in one format
  * Equal signs will have spaces on both sides, and operators with 2 characters will not have a space between those 2 characters
  * There are no repeating instruments
  * Only the function datediff() has been used in branching logic
  * The function will output a data frame with a list of queries based on the Data Dictionary.
  
  
```{r run}
# Run script
dir = "/Users/goings/Documents/Classes/B581 Biostatistics Computing/Final Project"
setwd(dir)
querylist <- REDCapQC(getwd(), "MIND_20231105.Rda")

# Summary of queries generated
table(querylist$var, querylist$txt)
head(querylist)
```
